DDSAnalytics  - Employee Trends

### 2018-04-16 msds6371-group-project-kaggle.Rmd
merge lokeshs changes

## Question 2

### Model Selection

@@

@@

### Comparison of Models
| Predictive Models | Adusted R^2 | CV Press | Kaggle Score |
|-------------------|:-----------:|:--------:|:------------:|
| Forward           | 0.1111      | 1111     | .111         |
| Backward          | 0.2222      | 2222     | .222         |
| Stepwise          | 0.3333      | 3333     | .333         |
| Custom            | 0.4444      | 4444     | .444         |

>>>>

\pagebreak

## Question 2
### The Problem
Ames Century 21 real estate would like us to perform the following analysis of homes:

Build the most predictive model for sales prices of homes in all of Ames Iowa.  By using  4 models: one from forward selection, one from backwards elimination, one from stepwise selection, and one the build custom.

The custom model is one of the three preceding models .  The  custom model  is the best in terms of being able to predict future sale prices of homes .

### Model Selection Process

1. We ran heat map of corelation between sales price and the different numerical variables 
2. we shortlisted the  variables that has highest corelation with Sales price.
3. Then we did log transformation on all numberic variables  and again check the corelation with sales price.Then identified some more 
   varaibles that has heigh corelation with sales price.
4. After performing above step, we identify to 10 variables that has high correlation with sales price.
5. Then we did the matrix scatter plot between these 10 variables and sales price, to visualize the correlation between sales price and     these variables; and visualize the correlation between explanatory variables.
6. We also found that among categorical variable ,neighbor hood and sales condition were relevant to predict the sales price . Adding them to the model , increased adjusted r^2 and decreased the RMSE. 
7. We removed outlier in variable GrLivArea that has < 4000 and all the relevant  variable is given to subset selection process.
7. We selected the model that has lowest cp score.That are Neighborhood, Sale Condition, OverallQual, LogLotArea, LogGrLiving, LogGarArea, LogTotalBsmtSF  and YearBuilt.
8. We  passed the same variable to  Forward/Backward/Stepwise  and we got same parameters back . All were significant.
9. We ran this model in SAS to validate model assumptions and we found the observations( # 31,411,632 and 1417) having high Studentized residuals that has 5 SD away. We investigated these observations and decided to delete them.
10 . Then reran the model and found out that all the assumptions has met
11. We ran the cross validation on the traing data set  and then obtain relevant cv test score.
12. We added sales price column to test data set,then ran the model . The observations and Predictions are inserted into a result data set, which was presented to Kaggles and results were given by Kaggle score . The results are shared in conclusion section.

@@

##### Assumptions
The Forward selection model is satisfying all below condition after performing transformation on some of the variables.
* Linear Trend (Plots: Response vs Explanatory, Explanatory vs Explanatory)
* Normality (Residual: Scatter, QQ Plot, Histogram)
* Equal Standard Deviation (Residual Scatter Plots)

@@

### Comparison of Models
| Predictive Models | Adusted R^2 | CV Press | Kaggle Score |
|-------------------|:-----------:|:--------:|:------------:|
| Forward           | 0.8801      | 23.2     | .201         |
| Backward          | 0.8801      | 23.2     | .201         |
| Stepwise          | 0.8801      | 23.2     | .201         |
| Custom*           | 0.8801      | 23.2     | .201         |

 * custom method choosen was Forward(select=SL)
### Conclusion
Based on above table , all the models selection is derving similar results . Any way we are going ahead with Stepwise model for deriving conclusion.

LogSalePrice=Neighborhood SaleCondition OverallQual LogLotArea LogGrLiving LogGarArea LogTotalBsmtSF YearBuilt

This model has adjusted R^2 =.8801 , CV Press=23.2  and RMSE=.021 , this model fulfill all the assumptions of the multiple linear regression , that are 
1. Residual: Scatter, QQ Plot, Histogram
2. Equal Standard Deviation (Residual Scatter Plots)
3. Cooks D is looking good.
4. We assums there is independence.

The Kaggle score is .201
\pagebreak
